%% 根据自己实际情况增加或删减
\begin{publications}
\noindent
\renewcommand{\labelenumi}{[\arabic{enumi}]}
\begin{spacing}{1.25}
\begin{enumerate}
\item \textbf{Wancheng Zhang}, Mingkun Zheng, Yong Liu, Zhenhua Zhang, Rui Xiong, and Zhihong Lu. Strain-induced nonrelativistic altermagnetic spin splitting effect[J]. Physical Review B, 2025, 112, 024415.
\item \textbf{Wancheng Zhang}, Mingkun Zheng, Yong Liu, Pan Zhang, Zhenhua Zhang, Rui Xiong, and Zhihong Lu. Unconventional spin Hall effect in rutile ${\mathrm{Cr}}_{0.5}{X}_{0.5}{\mathrm{O}}_{2}$ $(X=\mathrm{Ti},\mathrm{V},\mathrm{Os},\mathrm{Fe})$[J]. Physical Review B, 2024, 110(21), 214419.
\item \textbf{Wancheng Zhang}, Mingkun Zheng, Yong Liu, Rui Xiong, Chao Zuo, Meng Chen, Zhenhua Zhang, and Zhihong Lu. Oxygen-vacancy-mediated efficient charge-to-spin conversion in heavy-metal oxides[J]. Journal of Physics D: Applied Physics. (Under review).
\item Mingkun Zheng, \textbf{Wancheng Zhang}, You Lv, Yong Liu, Rui Xiong, Zhenhua Zhang, and Zhihong Lu. Observation of thickness-modulated out-of-plane spin-orbit torque in polycrystalline few-layer $T_d$-\ce{WTe2} film[J]. Nanomaterials, 2025, 15(10), 762.
\item Mingkun Zheng, \textbf{Wancheng Zhang}, You Lv, Yong Liu, Rui Xiong, Zhenhua Zhang, and Zhihong Lu. Low-temperature fabrication, magnetoresistance and spin pumping studies of polycrystalline few-layer 1$T$'-\ce{MoTe2} films. Journal of Alloys and Compounds, 2025, 1015, 178775.
\item Jindi Feng, \textbf{Wancheng Zhang}, Kunpeng Li, Mingkun Zheng, Yong Liu, Chao Zuo, Meng Chen, Dengjing Wang, Youyuan Yuan, Ke Wang, Zhenhua Zhang, Rui Xiong, and Zhihong Lu. Tailoring of band alignments and magnetic properties in two-dimensional \ce{CrBr3}/\ce{MoS2} van der Waals heterobilayer. Computational Materials Science, 2024, 236, 112862.
\item Kunpeng Li, Jindi Feng, \textbf{Wancheng Zhang}, Zhenhua Zhang, Rui Xiong, and Zhihong Lu. Enhancing spin splitting by symmetry and molecular orbital hybridization in \ce{VO2}. Computational Materials Science, 2023, 222, 112100.
\item Jindi Feng, Kunpeng Li, Mingkun Zheng, \textbf{Wancheng Zhang}, Yong Liu, Dengjing Wang, Zhenhua Zhang, Chao Zuo, Rui Xiong, and Zhihong Lu. Excellent spin-filtering and giant tunneling magnetoresistance in a dual-electrode van der Waals magnetic tunnel junction based on ferromagnetic \ce{CrSe2}. Applied Surface Science, 2023, 611, 155588.
\end{enumerate}
\end{spacing}
\end{publications}
